### 2016-09-30 results.tex
added OW attack and theorem for gbf

\todo{OW privacy proof? [JON]}

@@

Switching now to the case of a \emph{private}~$M$ GBF, i.e., $\pubaux=\emptystring, \privaux=\langle M \rangle$, we have the
following correctness bound.
\fixme{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
\begin{theorem}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ garbled Bloom filter. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
\]
\end{theorem}

@@

\begin{theorem}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the public~$M$ garbled Bloom filter, in the random-oracle model for~$H$.  Then 
\[
\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - (1-1/2^{\mu})^{q}
\]
 where $\mu = H_\infty(\distr{}{})$ is the pointwise min-entropy of~$\distr{}{}$, and $A_{\mathrm{ow}}$ makes $kq$ random-oracle queries.
\end{theorem}
%\begin{eqnarray*}
%\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} &=& 1 - \Prob{X_1 \not\in S \wedge X_2 \not\in S \wedge \cdots \wedge X_{q+1}\not\in S} \\
%&=& 1 - \prod_{i=1}^{q+1} \Prob{X_i \not\in S \,|\, X_{i-1} \not\in S \wedge \cdots X_1 \not\in S}\Prob{X_1 \not\in S}\\
%\end{eqnarray*}

>>>>

\todo{OW privacy proof? Attack? [JON]}

@@

Switching now to the case of a \emph{private}~$M$ GBF, i.e., $\pubaux=\emptystring, \privaux=\langle M \rangle$, we have the
following correctness bound.

\begin{theorem}\fixme{FINISH! (Animesh?)}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ garbled Bloom filter. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
\]
\end{theorem}

@@

\begin{theorem}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the public~$M$ garbled Bloom filter, in the random-oracle model for~$H$.  Then 
\[
\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - \left(1-\frac{1}{2^{\mu}} \right)^{q} \geq 1 - e^{-q/2^\mu}
\]
 where $\mu = H_\infty(\distr{}{})$ is the pointwise min-entropy of~$\distr{}{}$, and $A_{\mathrm{ow}}$ makes $kq$ random-oracle queries.
\end{theorem}

\todo{If time:  would be great to have an upperbound on onewayness for this construction!}
